\documentclass[a4paper, twoside, 12pt, noanswers]{exam}


% \documentclass[a4paper, 12pt, answers]{exam}
\usepackage{fontspec}

\usepackage{polyglossia}
\usepackage{dirtytalk}
\usepackage{enumitem}
\usepackage{fancybox}
\usepackage{multicol}
\usepackage{framed}
\usepackage{enumitem}
\usepackage{enumerate}
\usepackage{afterpage}
\newcommand\blankpage{%
    \null
    \thispagestyle{empty}%
    \addtocounter{page}{-1}%
    \newpage}

\setdefaultlanguage{english} 


\setotherlanguage{hindi} 
\newfontfamily\devanagarifont[Script=Devanagari]{Shobhika} %fonts-> Shobhika, Mukta, Kalimati, Lohit Devanagari, Lohit Nepali
\defaultfontfeatures{Ligatures=TeX}

\newcommand{\textnp}{\texthindi}
\newenvironment{nepali}{\begin{hindi}}{\end{hindi}}
\newcommand{\cs}{C\texttt{\#}}


\usepackage[onehalfspacing]{setspace}
\usepackage{graphicx}
\usepackage{multicol,adjustbox}

% \pointsinrightmargin %points in right margin
% \bracketedpoints

\nopointsinmargin %removes points from margin
\pointformat{} 

\unframedsolutions %do not show frame outside of solution


\CorrectChoiceEmphasis{\bfseries\boldmath} 
\renewcommand{\thepartno}{\alph{partno}} 
\renewcommand{\thesubpart}{(\roman{subpart})}
\renewcommand{\subpartlabel}{\thesubpart} 
\renewcommand{\choicelabel}{(\alph{choice})}

\thispagestyle{empty}

\cfoot[]{}
\clearpage

\begin{document}

%%%%%%Purbanchal University-2018%%%%%%
% 									 %															
%				2018				 %
%									 %
%%%%%%Purbanchal University-2018%%%%%%
\begin{framed}
	\raggedright{\bfseries\Large\centering PURBANCHAL UNIVERSITY \par {2018/ \textnp{२०७५}}\par}
	{ 4 Years Bachelor of Computer Application (BCA/Eighth Semester/Final)\par}
	{ Time: 3.00 hrs.  \hfill Full Marks: 60 / Pass Marks: 24\par}
	{\bfseries {BCA453CO, Dot Net Programming\hfill}\par}
\end{framed}

{\noindent \it{Candidates are required to give their own answers in their own words as far as practicable.  }\par}
{\noindent \it{Figure in the margin indicate full marks.}\par}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%				GROUP   A	
{\fullwidth{\centering \bfseries \underline{Group A}}}
{\hspace*{-0.5cm} \bfseries Answer TWO questions.} \hfill {\( \mathbf{2\times 12 =24}\)}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{questions}

	\question What are the components of NET framework? How do you implement
	OOP in \cs? Explain with example.

	\question What is ADO.NET? Explain ADO.NET architecture. Write a
	program to insert, delete and update employee records (Name,
	Age, Address, and Basic Salary) in database with proper
	validation. 2+4+6

	\question
	\begin{parts}
		\part What is hosting? Write about IIS Web Server and its features
		\part What is the use of data bound control in web application? Give
		example.
	\end{parts}


	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	%				GROUP   B					
	{\fullwidth{\centering \bfseries \underline{Group B}}\par}
	{\hspace*{-0.5cm}\noindent\bfseries Answer SIX questions.} \hfill {\( \mathbf{6 \times 6 = 36}\)}
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

	\question What are feature of VB.net? Explain event handling in \cs with
	example.

	\question What is a constructor? How do you overload methods in
	VB.NET?

	\question What do you mean by concurrency control? How is concurrency
	control resolved and maintained in ADO.NET? Explain with
	example.

	\question Write a program to demonstrate the use of smart tags.

	\question Explain data grid control used in .NET programming with
	example.

	\question Write a VB.NET client application and incorporate the necessary
	validations.

	\question Write notes on any TWO:
	\begin{parts}
		\part Cross language architecture
		\part Namespace
		\part .NET class libraries
	\end{parts}

\end{questions}
\newpage


%%%%%%Purbanchal University-2019%%%%%%
% 									 %															
%				2019				 %
%									 %
%%%%%%Purbanchal University-2019%%%%%%

\begin{framed}
	\raggedright{\bfseries\Large\centering PURBANCHAL UNIVERSITY \par {2019/ \textnp{२०७६}}\par}
	{ 4 Years Bachelor of Computer Application (BCA/Eighth Semester/Final)\par}
	{ Time: 3.00 hrs.  \hfill Full Marks: 60 / Pass Marks: 24\par}
	{\bfseries {BCA453CO, Dot Net Programming \hfill}\par}
\end{framed}

{\noindent \it{Candidates are required to give their own answers in their own words as far as practicable.  }\par}
{\noindent \it{Figure in the margin indicate full marks.}\par}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
{\fullwidth{\centering \bfseries \underline{Group A}}}
{\hspace*{-0.5cm} \bfseries Answer TWO questions.} \hfill {\( \mathbf{2\times 12 =24}\)}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{questions}
	\question Describe Architecture of NET Framework. Explain Just in Time
	compilation of managed code.
	\question What do you mean by polymorphism? Describe with its types and
	example.
	\question Write a program for Electricity Bill Statement (EBS). The EBS
	takes units consumed from consumer and calculates; Electricity
	Charges (EC) using provided criteria:
	\begin{subparts}
		\subpart Units less than 100  Rs 500 minimum charge.
		\subpart Units 100 above 300 below Rs 15 (per unit + minimum
		charge).
		\subpart Units above 300 Rs 25 (per unit + minimum charge).
	\end{subparts}


	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	{\fullwidth{\centering \bfseries \underline{Group B}}\par}
	{\hspace*{-0.5cm}\noindent\bfseries Answer SIX questions.} \hfill {\( \mathbf{6 \times 6 = 36}\)}
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

	\question What is the difference between a class and an object, and how do
	these terms relate to each other? Explain briefly with examples?
	\question List different features of .\ NET Technology. What does `managed
	code' means in .\ NET context?
	\question What are the difference between Radio Button control and Check
	Box control? Explain with an example.
	\question Why do we use String Builder in place of String in \cs .\ NET? Differentiate between string and String Builder.
	\question Explain ADO.NET, its features and architecture.
	\question Print the following pattern:

	\begin{mbox}
		\raggedright
		2\\
		3	5\\
		7	11	13	\\
		17	19	23	29\\
		31	37	41	43	47\\
	\end{mbox}

	\question What is array? Explain types of array with example.

	\question Write notes on any TWO:
	\begin{parts}
		\part Base Class Library
		\part Boxing and Unboxing
		\part Inheritance
	\end{parts}


% \nomorequestions

\end{questions}
\afterpage{\blankpage}
\end{document}
